COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-10-08 main.tex
Add discussion of figure 4, update plots with newly run EJ simulation

An additional effect that the MMRs have on the orbits of planetesimals is visible in figure \ref{fig:long_ph}. This shows the semimajor axis distribution of planetesimals as a function of longitude of perihelion in the EJ simulation. As discussed in section \ref{sec:sec_force}, the eccentric orbit of Jupiter causes the perihelia of the planetesimal orbits to align with the giant perturber. The mean motion resonances, however, drive the rather vigorous precession of the orbits of planetesimals in their vicinity. Because the timescale of the resonances is much shorter than the timescale for secular forcing, the longitudinal orientations of orbits close to the MMRs are effectively randomized. The dashed horizontal lines in figure \ref{fig:long_ph} indicate the libration width of the MMRs at the forced eccentricity (given by the magnitude of equation \ref{eq:eforced}. The size of the zone of vigorous precession roughly matches the libration width of the MMRs. As will be discussed in the next session, the relative longitudinal orientation of the orbits has important implications for where and when planetesimal collisions occur at a given semimajor axis.

>>>>

An additional effect that the MMRs have on the orbits of planetesimals is visible in figure \ref{fig:long_ph}. This shows the semimajor axis distribution of planetesimals as a function of longitude of perihelion in the EJ simulation. As discussed in section \ref{sec:sec_force}, the eccentric orbit of Jupiter causes the perihelia of the planetesimal orbits to align with the giant perturber. The mean motion resonances, however, drive the rather vigorous precession of the orbits of planetesimals in their vicinity. Because the timescale of the resonances is much shorter than the timescale for secular forcing, the longitudinal orientations of orbits close to the MMRs are effectively randomized. The dashed horizontal lines in figure \ref{fig:long_ph} indicate the libration width of the MMRs at the forced eccentricity (given by the magnitude of equation \ref{eq:eforced}. The size of the zone of vigorous precession roughly matches the libration width of the MMRs. As will be discussed shortly, the relative longitudinal orientation of the orbits has important implications for where and when planetesimal collisions occur at a given semimajor axis. Not shown is the longitude of perihelia and semimajor axes of the bodies in the CJ simulation. Due to the lack of secular forcing, the orientations of the orbits of these bodes are effectively random.

Next, we move on to examine the statistics of the collisions that occur. Figure \ref{fig:coll_hist_a} shows the distribution of semimajor axes of every collision that is resolved. Here, the semimajor axis of a collision is defined as the semimajor axis of the first body participating in the collision at the moment that it occurs. During a collision, the determination of which body is first and which is second is determined by the collision search tree in {\sc ChaNGa}. To ensure that this does not introduce any bias, we also constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference. By examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates. The dashed lines again represent the libration width of each resonance and are meant to show its range of influence. In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR. Interestingly, the 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation. (Better check if this is still true when I rerun CJ with smaller steps). In both cases, the 5:3 MMR appears to slightly enhance the collision rate interior to the nominal resonance location. It is important to keep in mind, however that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce nonphysical boundary effects.
